Neon: Nuclear Norm to Beat Muon

### 2025-04-26 article/muon.tex
fixed references
changed sentence structure in first paragraph of the section

\section{Idea}
The goal of the project is to make variations on Muon to speed it up. Recently, authors of \cite{bernstein2024oldoptimizernewnorm} have proposed to look at different optimizers as the solution of the optimization problem for an update. This approach can be utilized to derive Muon \cite{jordan2024muon}, a novel algorithm for fast training of neural networks. Instead of using spectral norm in the problem, we use nuclear norm to produce a new problem. %Then, we add momentum to update. After finalizing the algorithm, we test it on MLP, and, if results are satisfactory, on transformers (probably something from huggingface). The result will be a fast algorithm, which we will convert into a new optimizer class for PyTorch, as was done with Muon.%

@@

\bibliographystyle{unsrt}
\bibliography{muon}

>>>>

\section{Idea}
The goal of the project is to make variations on Muon to speed it up. Recently, authors of \cite{bernstein2024oldoptimizernewnorm} have proposed a framework, which allows to describe update step of many optimizers as the solution of the certain optimization problem. This approach can be utilized to derive Muon \cite{jordan2024muon}, a novel algorithm for fast training of neural networks. We change optimization problem defining update step of Muon slightly. Instead of using spectral norm in the optimization problem, we use nuclear norm to produce a new problem and a new algorithm. %Then, we add momentum to update. After finalizing the algorithm, we test it on MLP, and, if results are satisfactory, on transformers (probably something from huggingface). The result will be a fast algorithm, which we will convert into a new optimizer class for PyTorch, as was done with Muon.%

@@

\bibliographystyle{unsrt}
\bibliography{muon.bib}
